---
title: "課?<a0>?練習模<e7><89><88>"
author: "tom0410"
date: "2020-12-27"
output: output_format
params:
  id: "410973093"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Your code

##5.2.1 if
```{r}
set.seed(10739)
customers <- data.frame(
  bills = sample(200:500, 10),
  vouchers = sample(c(T,F), size=10, replace=T,
                     prob=c(0.4,0.6)
                     )
)
head(customers)
```

```{r}
bill <- customers$bills[[3]]
hasVoucher <- customers$vouchers[[3]]
totalBill <- 
{
  startingBill <- bill
  if(hasVoucher)
  {
    bill <- bill - 20
  }
  message("You initial bill is ", startingBill,".\n",
          "You final bill is ", bill)
  bill
}
print(totalBill)
```

###用function(   ,   )整個打包
```{r}
get_totalBill <- function(bill, hasVoucher) ###function()
{
  startingBill <- bill
  if(hasVoucher)
  {
    bill <- bill - 20
  }
  message("You initial bill is ", startingBill,".\n",
          "You final bill is ", bill, "\n")
  bill
}

get_totalBill(
  customers$bills[[5]],
  customers$vouchers[[5]]
)
```

###map
```{r}
library(stringr)
library(purrr)
map(
  1:10,
  ~{
    get_totalBill(
  customers$bills[[.x]],
  customers$vouchers[[.x]]
    )
  }
)
```

###map2
```{r}
purrr::map2(
  customers$bills, customers$vouchers,
  ~get_totalBill(.x, .y)
)
```

`f(x) = sqrt(x), x >= 0`
```{r}
f <- function(x){
  if(x<0)
  {
    stop("x has to be non-negative.")
  }
  sqrt(x)
}

f(-2)
f(2)
```

```{r}
comment_grade <- function(grade){
  if(grade < 60) return("Don't give up. There is still hope.")
  return("Good job. Keep going")
}
```

```{r}
comment_grade(55)
comment_grade(70)
```

```{r}
df_grades <- data.frame(
  grade=sample(50:95, 20, replace = T)
)
purrr::map_chr(
  df_grades$grade,
  comment_grade
) -> df_grades$comment
```

```{r}
unlist(map(
  df_grades$grade,
  comment_grade
))
```

##5.2.2 condition
Use
###all() 
to flag if `all` failed.

###any() 
to flag if `any` failed.
```{r}
grades <- c(72, 55, 82)
# any one failed? 
if(any(grades < 60)) message("\nYes, someone failed")
```

```{r}
Sys.setenv("_R_CHECK_LENGTH_1_CONDITION_" = "true")
```

```{r}
grades <- c(55, 72, 82)
# any one failed? 
if(grades < 60) message("\nYes, someone failed") # error now
```

##5.2.3 && ||

###&&
```{r}
grade1 <- list(
  economics=55,
  calculus=77
)
grade2 <- c(
  economics=55,
  calculus=77
)
```

```{r}
(is.list(grade1) &  grade1$economics > 60) #False
(is.list(grade2) &  grade2$economics > 60) #error (因為grade用的是`c()`
```

`&&`:
Conditions are check sequentially. `When one is FALSE, there is no need to check subsequent conditions`; a FALSE is concluded.
```{r}
(is.list(grade1) && grade1$economics > 60) #FALSE
(is.list(grade2) && grade2$economics > 60) #FALSE
```
###||
```{r}
myAge <- 75

if(myAge >=65 | stop("Error")){
  "Qualified"
} else {
  warning("Not qualified")
}

#error: Error
```
`||`:
Conditions are check sequentially. `When one is TRUE, there is no need to check subsequent conditions`; a TRUE is concluded.
```{r}
if(myAge >=65 ||  stop("Error")){
  "Qualified"
} else {
  warning("Not qualified")
}

#"Qualified"
```

##5.2.4 if else

```{r}
fx <- function(x)
{
  # ending scenario 1:
  if(x %% 2 ==0) #x is even
  {
    return(x/2)
  } else
  # ending scenario 2:
  {
    return(-(x+1)/2)
  }
}
```

```{r}
fx(4L)
fx(7L)
```
##5.2.5 if-else if-else if-else

e.g.
成績等級：

90以上: 優 # condition A

80-89：良 # condition B

70-79：尚可 # condition C

70以下：待加強 # else
```{r}
# 前提
grade <- 88
# 任務
comment <- 
{
  {
    "優"
  }
  {
    "良"
  }
  {
    "尚可"
  }
  {
    "待加強"
  }
}
```

```{r}
# 前提
grade <- 88
# 任務
comment <- 
{
  if(grade>=90)
  {
    "優"
  } else
  if(grade >=80 && grade <=89)
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment #"良"
```

```{r}
comment_grade <- function(grade){  #function()
  if(grade>=90)
  {
    "優"
  } else
  if(grade >=80 && grade <=89)
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment_grade[c(90,85)]
```
***If there are multiple TRUE flags from different if-condition expressions, ONLY the programming block `follows the FIRST TRUE flag will be executed`
```{r}
comment_grade <- function(grade){
  if(grade>=85)
  {
    "優"
  } else
  if(grade >=80 && grade <=89) 
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment_grade(86)
```

##5.2.6 switch
```{r}
sortedEmails <- list(
  office=character(),
  student=character(),
  private=character()
)
```

```{r}
set.seed(2839)
emailFrom <- sample(
  c("econ@gm.ntpu.edu.tw","classStudents@gm.ntpu.edu.tw","xxx@gmail.com","econStaff@gm.ntpu.edu.tw","yyyy@gmail.com"), 50,
  replace=T
)
head(emailFrom, 10)
```

```{r}
.x<- 3
commingEmail <- emailFrom[[.x]]
```

```{r}
# Office
{
  message("You have a message from office.")
  nOffice <- length(sortedEmails$office)
  sortedEmails$office[[nOffice+1]] <- commingEmail
  sortedEmails
}
# Student
{
  message("There is an email from student in your class.")
  nStudent <- length(sortedEmails$student)
  sortedEmails$student[[nStudent+1]] <- commingEmail
  sortedEmails
}
# Private
{
  message("A private message has come in.")
  nPrivate <- length(sortedEmails$private)
  sortedEmails$private[[nPrivate+1]] <- commingEmail
  sortedEmails
}
```

```{r}
library(stringr)
condition_sgn <- 
  ifelse(
    str_detect(commingEmail,"econ"), "office", commingEmail)
```

```{r}
switch(
  condition_sgn,
  "office"={
    message("You have a message from office.")
    nOffice <- length(sortedEmails$office)
    sortedEmails$office[[nOffice+1]] <- commingEmail
    sortedEmails
  },
  "classStudents@gm.ntpu.edu.tw"={
    message("There is an email from student in your class.")
    nStudent <- length(sortedEmails$student)
    sortedEmails$student[[nStudent+1]] <- commingEmail
    sortedEmails
  },
  {
    message("A private message has come in.")
    nPrivate <- length(sortedEmails$private)
    sortedEmails$private[[nPrivate+1]] <- commingEmail
    sortedEmails
  }
)
```

